Maragra-CISM status report

### 2017-08-29 inst/rmd/maragra_preliminary_analysis.Rmd
adding census

```{r}
# Read in data
ab <- maragra::ab
ab_panel <- maragra::ab_panel
clinic <- maragra::clinic
clinic_agg <- maragra::clinic_agg
mc <- maragra::mc
workers <- maragra::workers
```

>>>>

```{r}
# Read in data
ab <- maragra::ab
ab_panel <- maragra::ab_panel
census <- maragra::census
census_sp <- maragra::census_sp
clinic <- maragra::clinic
clinic_agg <- maragra::clinic_agg
mc <- maragra::mc
workers <- maragra::workers
```
